%!TEX root = main.tex

\abstract{
Fuzzy extractors convert noisy signals from the physical world into reliable cryptographic keys.  %An
                                                                                                  %important
                                                                                                  %open
                                                                                                  %question
                                                                                                  %is
                                                                                                  %building
                                                                                                  %fuzzy
                                                                                                  %extractors
                                                                                                  %that
                                                                                                  %secure
                                                                                                  %all
                                                                                                  %possible
                                                                                                  %distributions.
Fuzzy min-entropy is an important measure the ability of a fuzzy
extractor to distill keys from a distribution: in particular, it
bounds the length of the key that can be derived (Fuller, Reyzin, and
Smith, IEEE Transactions on Information Theory 2020).
%Specifically, fuzzy
%min-entropy is proportional to the sum of the probability of nearby
%points, such points are transformed to the correct key and suffice for
%adversary success.
In general, fuzzy min-entropy that is superlogarithmic in the security
parameter is required for a noisy distribution to be suitable for key
derivation.
 
There is a wide gap between what is possible with respect to
computational and information-theoretic adversaries.  Under the
assumption of general-purpose obfuscation, keys can be securely
derived from all distributions with superlogarithmic entropy.
%% I am confused about "obfuscator" here.
Against information-theoretic adversaries, however, it is impossible
to build a single fuzzy extractor that works for all distributions
(Fuller, Reyzin, and Smith, IEEE Transactions on Information Theory
2020).

A weaker information-theoretic goal is to build a fuzzy extractor for
each particular probability distribution.  This is the approach taken
by Woodage et al. (Crypto 2017).  Prior approaches use the full
description of the probability mass function and are inefficient.  We
show this is inherent: \textbf{for a quarter of distributions with
  fuzzy min-entropy and $2^k$ points there is no secure fuzzy
  extractor that uses less $2^{\Theta(k)}$ bits of information about
  the distribution.}  This result rules out the possibility of
efficient, information-theoretic fuzzy extractors for most
distributions with fuzzy min-entropy.

We show an analogous result with stronger parameters for information-theoretic secure sketches. Secure sketches are frequently used to construct fuzzy extractors. 
}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:
